---
title: 'Most Inportant Chart for Investors'
output:
  html_document:
    highlight: pygments
    theme: spacelab
    toc: yes
    toc_depth: 3
---
<style type="text/css">
p{ /* Normal  */
   font-size: 14px;
   line-height: 18px;}
body{ /* Normal  */
   font-size: 14px;}
td {  /* Table  */
   font-size: 12px;}
h1 { /* Header 1 */
 font-size: 26px;
 color: #4294ce;}
h2 { /* Header 2 */
 font-size: 22px;}
h3 { /* Header 3 */
 font-size: 18px;}
code.r{ /* Code block */
  font-size: 12px;}
pre { /* Code block */
  font-size: 12px}
#table-of-contents h2 {
  background-color: #4294ce;}
#table-of-contents{
  background: #688FAD;}
#nav-top span.glyphicon{
  color: #4294ce;}
#postamble{
  background: #4294ce;
  border-top: ;}
</style>

```{r echo=FALSE, warning=F, message=F}
if(!require(easypackages)){install.packages("easypackages")}
library(easypackages)
packages("tidyverse", prompt = TRUE)
options(scipen = 1e9)

setwd("~/GitHub/Finance")
```

```{r}
source("https://raw.githubusercontent.com/KaroRonty/ShillerGoyalDataRetriever/master/ShillerGoyalDataRetriever.r")
```

```{r}
data <- full_data %>%
  # Change index_real to index to get the nominal returns
  select(dates, index_real) %>% na.omit()

# Calculate index for each year
index <- seq(1:nrow(data))

# Make a tibble for containing the years and returns
leaded <- as_tibble(matrix(NA, ncol = length(index), nrow = nrow(data)))
# Rename columns
colnames(leaded) <- paste0("m", 1:length(index))

# Loop future i month returns
for (i in index) {  leaded[, i] <- lead(data$index, i) / data$index}

# Calculate prediction intervals
quantiles <- cbind(sapply(leaded %>% select(m1:m600),
                          function(x) quantile(x, na.rm = T, 0.05)),
                   sapply(leaded %>% select(m1:m600),
                          function(x) quantile(x, na.rm = T, 0.95)))

# Format data
quantiles <- quantiles %>% as.data.frame() %>% rownames_to_column(var = "key") %>%
      rename(min = V1, max = V2) %>% mutate(key = str_remove(key, ".5%"))

# Gather & attach prediction intervals
to_plot <- leaded %>% select(m1:m600) %>% gather() %>% left_join(quantiles)

```

```{r}
# Format years, rename and plot
to_plot %>%
  mutate(key = as.numeric(str_remove(key, "m"))) %>%
  rename(Year = key,
         Multiple = value) %>%
  mutate(Year = as.numeric(fct_reorder(as.character(Year), sort(Year))) / 12) %>%
  ggplot(aes(x = Year,
             y = Multiple)) +
  stat_smooth(color = "black") +
  geom_point(color = "#00BFC4", alpha = 0.01) +
  scale_y_continuous(breaks = c(0.5, 1, 2, 4, 8, 16, 32, 64, 128),
                     trans = "log") +
  ggtitle("Historical inflation-adjusted S&P 500 returns") +
  xlab("Years invested") +
  geom_line(aes(y = min), color = "black") +
  geom_line(aes(y = max), color = "black") +
  theme(panel.grid.major = element_line(color = "#969696", size = 0.25))
```


Time is the investor's best friend. The longer the investment horizon, the less the investment returns depend on factors such as crashes and current valuation levels. It is known that the chance for losing in the stock market on a 20-year period has historically been about zero. This post attempts to expand on this fact and take a look at how risky the U.S. stock market has actually been for long-term investors.

As usual, we'll use data from Robert Shiller to answer the questions. The data begins from the year 1871, long before the actual S&P 500 index was created. We'll only consider lump-sum investing, since dollar cost averaging is another story.

Let's first look at the inflation-adjusted returns for an U.S. investor, including reinvested dividends.  Keep in mind, that the U.S. stock market has been one of the best performing in the world, and future returns are likely to be lower because of high valuations and lower productivity and population growth. The upper and lower bands are the 95 percent prediction intervals, i.e. 95 percent of the time the investment return has been between these bands. The y-axis tells how many times your investment would have been multiplied. Notice that the axis is logarithmic.


This chart demonstrates how uncertain investing is. The range of outcomes is very large, but it doesn't necessarily tell the full truth. France once had a 66-year period where stocks didn't beat inflation, for Italy the longest streak was 73 years and for Austria a painful period of 97 years. This is why global diversification is important. There has however been a 5 percent chance that the investment would have increased 64-fold in the U.S. for the same period. The risk works both ways.


The inflation in the U.S. has been quite high, over three percent annually. Inflation of course affects different companies in a different way, but the net effect is that lower inflation does not necessarily lead to higher inflation-adjusted ret