
---
title: "Visualizations for Algorithmic Trading in R"
output:
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
if(!require(easypackages)){install.packages("easypackages")}
library(easypackages)
packages("PortfolioEffectHFT", "rvest", "pbapply", "TTR", "dygraphs", "lubridate", "timetk", "pacman", 
         "quantmod", "parallelMap", "BiocParallel", "parallel", "plotly", "DT",  prompt = F)
set.seed(123)
```

```{r}
## Install BiocParallel
source("https://bioconductor.org/biocLite.R")
biocLite("BiocParallel")
```

# Introduction

Visualizations for Algorithmic trading is rising in demand by the economic sector. In R there are a lot of great packages for getting data, visualizations and model strategies for algorithmic trading. In this article, you learn how to perform visualizations and modeling for algorithmic trading in R.

Algorithmic trading is a very popular machine learning method within the economic and financial sector. Typically it involves a lot of programming in advanced visualizations and modelling. The programming is necessary in order to get the financial data for the Algorithmic Trading analysis. This article involves the first part of Algorithmic trading: Advanced Visualizations.

# Data

```{r}
# Data Collection
website <- read_html("https://www.marketwatch.com/tools/industry/stocklist.asp?bcind_ind=9535&bcind_period=3mo")
table <- html_table(html_nodes(website, "table")[[4]], fill = TRUE)
stocks.symbols<-table$X2
stocks.names<-table$X3
table1<-table[-1,-1]
colnames(table1)<-table[1,-1]
DT::datatable(table1)
stock.list<-"https://www.marketwatch.com/tools/industry/stocklist.asp?bcind_ind=9535&bcind_period=3mo"
stocks<-read_html(stock.list)
stocks.names<-html_nodes(stocks,".lk01")
stocks.names<-html_text(stocks.names)
table1[table1==""] <- NA
table1<-table1[complete.cases(table1$Symbol),]
DT::datatable(table1)
# Date creation
start.date<-Sys.Date()
end.date<-Sys.Date()-years(3)
start.date<-gsub('-','', start.date)
end.date<-gsub('-','', end.date)
start.date
# The symbols vector holds our tickers. 
symbols <- c("SPY","EFA", "IJS", "EEM","AGG")
# The prices object will hold our raw price data 
prices %>%
  map(~Ad(get(.))) %>%   #Extract (transformed) data from a suitable OHLC object. getSymbols('IBM',src='yahoo') Ad(IBM)
  reduce(merge) %>%   #reduce() combines from the left, reduce_right() combines from the right
  `colnames<-`(symbols)
head(prices)
tickers <- c("AAPL", "MSFT","GOOGL","IBM","FB")
getSymbols(tickers)
closePrices <- do.call(merge, lapply(tickers, function(x) Cl(get(x))))
# Mapping
parallelStartSocket(2) 
parallelStartMulticore(cpus=6)# start in socket mode and create 2 processes on localhost
f = function(x) Cl(get(x))     # define our job
y = parallelMap(f, tickers) # like R's Map but in parallel
mapdata %>% head()
# Bioconductor
f = function(x) Ad(get(x))
options(MulticoreParam=quote(MulticoreParam(workers=4)))
param <- SnowParam(workers = 2, type = "SOCK")
vec=c(tickers[1],tickers[2],tickers[3],tickers[4])
multicoreParam <- MulticoreParam(workers = 7)
bio=bplapply(tickers, f, BPPARAM = multicoreParam)
biodata %>% head()
```

# Visualizations

```{r}
# Visualization graph
AdjustedPrices<-biodata
dateWindow %>%
  dyRebase(value = 100) %>%
  dyRangeSelector(dateWindow = dateWindow)
end<-Sys.Date()
start<-Sys.Date()-years(3)
prices  %>% head()
pacman::p_load(dygraph)
```

Calculate the number of cores in the data and apply this in the visualization graph.

```{r}
# Calculate the number of cores
no_cores <- detectCores() - 1
# Initiate cluster
cl <- makeCluster(no_cores)
f<-function(x) Ad(get(x))
AdjustedPrices %>% head()
# vISUALIZATION inkl number of cores
dateWindow %>%
  dyRebase(value = 100) %>%
  dyRangeSelector(dateWindow = dateWindow)
```

Before making the third visualisation we need to do some more programming:

```{r}
# QUANTITATIVE MODELLING
getSymbols("AAPL",src='yahoo')
# basic example of ohlc charts
df <- data.frame(Date=index(AAPL),coredata(AAPL))
df <- tail(df, 30)
# cutom colors
i <- list(line = list(color = '#FFD700'))
d <- list(line = list(color = '#0000ff'))
p %>%
  plot_ly(x = ~Date, type="ohlc",
          open = ~AAPL.Open, close = ~AAPL.Close,
          high = ~AAPL.High, low = ~AAPL.Low,
          increasing = i, decreasing = d)
p
```

Next let us make a programmed visualization of adjusted stock prices over time.

```{r}
# Programmed visualization of adjusted stock prices over time
biodatadf %>% rename(Date=index)
data %>% filter(Date>"2014-01-11")
p %>%
  add_trace(y = ~MSFT.Adjusted, name = 'MSFT', mode = 'lines')%>%
  add_trace(y = ~IBM.Adjusted, name = 'IBM', mode = 'lines')%>%
  add_trace(y = ~GOOGL.Adjusted, name = 'GOOGL', mode = 'lines')%>%
  layout(title = "Visualizing Adjusted Stock Prices",
         xaxis = list(title = "Time"),
         yaxis = list (title = "Adjusted Prices"))
p
```

# Simple Trading Strategy with Trend Following

Next we will program a visualization of interactive Apple Moving Avereges over time.

```{r}
## Simple Trading Strategy: Trend Following
tail(SMA(AdjustedPrices$AAPL.Adjusted, 200))
tail(SMA(AdjustedPrices$AAPL.Adjusted, 50)) 
data.frame(sma200=SMA(AdjustedPrices$AAPL.Adjusted, 200),sma50=SMA(AdjustedPrices$AAPL.Adjusted, 50)) %>% head()
sdata %>% select(-Date)
#sdata<-tk_xts(data,date_var=Date)
df_50=as.data.frame.matrix(apply(sdata, 2, SMA,50))
colnames(df_50)=paste0(colnames(df_50),"_sma50")
df_200=as.data.frame.matrix(apply(sdata, 2, SMA,200))
colnames(df_200)=paste0(colnames(df_200),"_sma200")
df_all %>% drop_na()
# sma 50
f50<- function(x) SMA(x,50)
# sma 50
f200<- function(x) SMA(x,200)
df_all %>% head()
dim(df_all)
# Moving avereges
mov.avgs<-function(df){
  
  ifelse((nrow(df)<(2*260)),
         x<-data.frame(df, 'NA', 'NA'),
         x<-data.frame( SMA(df, 200), SMA(df, 50)))
  colnames(x)<-c( 'sma_200','sma_50')}
  x %>% head()
var=names(df_all)[str_detect(names(df_all), "AAPL")]
df_all[,var] %>% head()
dateWindow=c("2015-01-01","2018-09-01")
dygraph(df_all[,var],main = 'Apple Moving Averages') %>%
  dySeries('AAPL.Adjusted_sma50', label = 'sma 50') %>%
  dySeries('AAPL.Adjusted_sma200', label = 'sma 200') %>%
  dyRangeSelector(height = 30) %>%
  dyShading(from = '2016-01-01', to = '2016-9-01', color = '#CCEBD6') %>%
  dyShading(from = '2016-9-01', to = '2017-01-01', color = '#FFE6E6')%>%
  dyRangeSelector(dateWindow = dateWindow)
```

https://datascienceplus.com/visualizations-for-algorithmic-trading-in-r/

